Supp mat: time series paper

### 2017-08-17 writing/manuscript_draft.Rmd
rewrote results section

---
bibliography: White_bib.bib
fontsize: 12pt
geometry: margin=1in
header-includes: \usepackage{float} \usepackage{setspace}\doublespacing \usepackage{lineno} \usepackage[firstinits=true,style=authoryear-comp,natbib=true,doi=false,isbn=false,url=false,uniquename=false,uniquelist=false,sorting=none]{biblatex}

@@

Addresses:\emph{$^1$ Center for Population Biology, University of California-Davis, Davis, California 95616 USA}
\vspace{3 mm}

$^2$Corresponding author: eawhite@ucdavis.edu
\vspace{3 mm}

Number of words: X,XXX (less than 4,000 words or 20 pages)
\vspace{3 mm}

@@

@@

# Abstract
Long-term census data are necessary to better understand ecological processes and make management decisions. However, census data are often expensive, requiring a lot of time and resources. Little work has addressed the question: when is a time series of census data long enough to address a question of interest? <!--Here, we explore two approaches to address this question: simulations and an empirical approach.--> We determine the minimum time series length required to estimate significant increases or decreases in population abundance. Importantly, we examine the ability to detect a trend with a set level of statistical power, which is often neglected in ecological time series analyses. Using a simulation approach, we demonstrate how the minimum time series length required increases with weaker trends in abundance and with higher population variability. In addition, we examine 878 populations of vertebrate species to determine the minimum time required to detect changes in their abundance. We show that 10-15 years of continuous monitoring are required in order to achieve a high level of statistical power. Similar to simulation-approaches, the minimum time required for field census data strongly depends on trend strength, population variability, and temporal autocorrelation. <!--Perhaps surprisingly, the minimum time required did not correlate well with biological explanatory variables, like body size or generation length.--> These results point to the importance of sampling populations over long periods of time. <!--We stress the need for verifying a study has enough statistical power to accurately determine long-term population trends.--> Time series less than 10-15 years are likely under-powered and potentially misleading.

@@

We also explored how the simulation approach can be applied to more biologically-realistic population models (Fig. \ref{fig:shark_example}). More specifically, we determine the minimum time required to estimate long-term population trends using a stochastic, age-structured model of lemon shark population dynamics in the Bahamas [@White2014]. We found that over 27 years of continuous monitoring were needed in this particular scenario (Fig. \ref{fig:shark_example}). Similar to the simulation approach decribed above, the minimum time required for the lemon shark population was strongly dependent on model parameters.

@@

We determined the minimum time series length ($T_{min}$) required to address a particular question of interest. More specifically we asked, what is the minimum time series length required to determine, via linear regression, the long-term population trend? Here, the minimum time series length required had high enough statistical power (greater than 0.8) for a set significance level of 0.05. We investigated this question through two approaches: simulation-based and empirical analyses. We briefly describe results from the simulation approach and then discuss our empirical approach.

@@

We constructed a general population model where the trend (i.e. slope coefficient) over time could be a model parameter. We chose a simple model, but any other population model could be used (Fig. \ref{fig:min_time_dist_log_pop}). Ideally, the specific model choice should be tailored to the population of interest. We then ran simulated time series of different lengths. From these simulations we determined the minimum time series length required to achieve a certain level of statistical power. We were also able to alter the parameter values (trend strength and population variability) of the population model to see how this altered $T_{min}$ (Fig. \ref{fig:theoretical_approach}).

In line with past work [@Gerrodette1987], we found the $T_{min}$ increases (i.e. more time is required) with decreases in trend strength and with increases in variability (Fig. \ref{fig:theoretical_approach}).

@@

We examined a database of `r nrow(pop_info)` separate population time series representing `r length(table(pop_info$Binomial))` species. This database consists of species with a variety of life history characteristics. We limited our analyses to populations with at least 35 years of continuous sampling. We examined the minimum time required to estimate long-term trends via linear regression.

Across all the populations we examined, we found an average minimum time series length required ($T_{min}$) of `r round(mean(pop_info$min_time_for_power),1)` ($\sigma$=`r round((var(pop_info$min_time_for_power))^0.5,1)`), with a wide distribution (Fig. \ref{fig:min_time_dist}). In addition, as expected based on our simulation results and those of others [@Rhodes2011], the minimum time series length required is strongly correlated with trend strength, population variance, and autocorrelation (Fig \ref{fig:correlates}). Using a generalized linear model, with a Poisson error structure, all three of these explanatory variables were significant and had large effect sizes (see Table S1). Combined, trend strength, population variance, and autocorrelation account for about `r round(100*(poisson_model$null.deviance - poisson_model$deviance)/(poisson_model$null.deviance),1)` of the explained deviance, which is similar to $R^2$ [@Zuur2009], in minimum time series length required.

We also examined a subset of populations where more explanatory variables were known (e.g. body mass, longevity, location). None of these explanatory variables were predictive of the minimum time series length required (Fig. \ref{fig:biological_correlates}). Some differences in $T_{min}$ did occur between biological class (Fig. \ref{fig:class}), but this can be attributed to the amount populations are known to fluctuate (i.e. the variability in population size).

@@

<!--Integrate with other sections
## Questions in the supplmentary material

In the supplementary material, we explore several additional questions related to statistical power and estimating $T_{min}$. First, we showed that other metrics besides estimating the slope coefficient from linear regression could be used. More specifically, we show how the same approach described here can be used to determine the minimum time required to estimate a population's geometric growth rate (Figs. \ref{fig:growth_rate},\ref{fig:min_time_growth_dist}). We also explored how the simulation approach can be applied to more biologically-realistic population models (Fig. \ref{fig:shark_example}). More specifically, we determine the minimum time required to estimate long-term population trends using a stochastic, age-structured model of lemon shark population dynamics in the Bahamas [@White2014]. We found that over 27 years of continuous monitoring were needed in this particular scenario (Fig. \ref{fig:shark_example}. Lastly, we determine the minimum time required to estimate long-term trends according to generalized additive models, instead of the simple linear models used here (Fig. \ref{fig:gam_example}). We found that although we obtain a similar distribution of minimum times required for GAMs, the minimum time required for GAMs is on average shorter than for linear regression (Fig. \ref{fig:min_time_dist_gam}). We expand on these results in the supplementary material.
-->

@@

 \setcounter{figure}{0}
 \renewcommand{\thefigure}{S\arabic{figure}}

>>>>

---
bibliography: White_bib.bib
fontsize: 12pt
geometry: margin=1in
header-includes: \usepackage{float} \usepackage{lineno} \usepackage[firstinits=true,style=authoryear-comp,natbib=true,doi=false,isbn=false,url=false,uniquename=false,uniquelist=false,sorting=none]{biblatex}

@@

Address:\emph{
    \\$^1$Center for Population Biology \\
    University of California, Davis \\
    2320 Storer Hall \\
		University of California, Davis \\
		One Shields Avenue Davis, CA, USA}
\vspace{3 mm}

$^2$Corresponding author: eawhite@ucdavis.edu, 1 480 203 7931
\vspace{3 mm}

Number of words (including 300 words for figures): X,XXX 
Number of figures:
Number of figures in supplementary material:
\vspace{3 mm}

@@

Color does not need to be used for any figures in print
\vspace{3 mm}

@@

\begin{abstract}
Long-term census data are necessary to better understand ecological processes and make management decisions. However, census data are often expensive, requiring a lot of time and resources. Little work has addressed the question: when is a time series of census data long enough to address a question of interest? <!--Here, we explore two approaches to address this question: simulations and an empirical approach.--> We determine the minimum time series length required to estimate significant increases or decreases in population abundance. Importantly, we examine the ability to detect a trend with a set level of statistical power, which is often neglected in ecological time series analyses. Using a simulation approach, we demonstrate how the minimum time series length required increases with weaker trends in abundance and with higher population variability. In addition, we examine 878 populations of vertebrate species to determine the minimum time required to detect changes in their abundance. We show that 10-15 years of continuous monitoring are required in order to achieve a high level of statistical power. Similar to simulation-approaches, the minimum time required for field census data strongly depends on trend strength, population variability, and temporal autocorrelation. <!--Perhaps surprisingly, the minimum time required did not correlate well with biological explanatory variables, like body size or generation length.--> These results point to the importance of sampling populations over long periods of time. <!--We stress the need for verifying a study has enough statistical power to accurately determine long-term population trends.--> Time series less than 10-15 years are likely under-powered and potentially misleading.
\end{abstract}

@@

@@

We determined the minimum time series length ($T_{min}$) required to address a particular question of interest. What is the minimum time series length required to determine, via linear regression, the long-term population trend? Here, the minimum time series length required had high enough statistical power ($1-\beta$ greater than 0.8) for a set significance level ($\alpha$) of 0.05. It is also possible to alter $1-\beta$ and $\alpha$. Predictably, as we increased our level of power or decreased $\alpha$, $T_{min}$ increased (Fig. \ref{fig:min_time_vs_alpha_beta}). We investigated this question through two approaches. We briefly describe results from the simulation approach and then discuss our empirical approach.

@@

We constructed a general population model where the trend strength (i.e. slope coefficient) over time could be a model parameter. We then ran simulated time series of different lengths. From these simulations we determined the minimum time series length required to achieve a certain level of statistical power. In line with past work [@Gerrodette1987], we found the $T_{min}$ increases (i.e. more time is required) with decreases in trend strength and with increases in population variability (Figs. \ref{fig:theoretical_approach}c,d).

We chose a simple model, but any other population model could be used (see example in Fig. \ref{fig:min_time_dist_log_pop}). Ideally, the specific model choice should be tailored to the population of interest. We explored how the simulation approach can be applied to more biologically-realistic population models (Fig. \ref{fig:shark_example}). More specifically, we determined the minimum time required to estimate long-term population trends using a stochastic, age-structured model of lemon shark population dynamics in the Bahamas [@White2014]. We found that over 27 years of continuous monitoring were needed in this particular scenario (Fig. \ref{fig:shark_example}). Similar to the simulation approach decribed above, the minimum time required for the lemon shark population was strongly dependent on model parameters.

@@

We examined a database of `r nrow(pop_info)` separate population time series representing `r length(table(pop_info$Binomial))` species. This database consists of vertebrate species with a variety of life history characteristics (Fig. \ref{fig:biological_correlates}). We limited our analyses to populations with at least 35 years of continuous sampling. We then examined the minimum time required to estimate long-term trends via linear regression.

Across all the populations we examined, we found an average minimum time series length required ($T_{min}$) of `r round(mean(pop_info$min_time_for_power),1)` ($\sigma$=`r round((var(pop_info$min_time_for_power))^0.5,1)`), with a wide distribution (Fig. \ref{fig:min_time_dist}). Estimates of $T_{min}$ varied between biological class (Fig. \ref{fig:min_time_dist}). Ray-finned fish (class Actinopterygii) typically had estimates of $T_{min}$ over 20 years. Birds (class Aves) had a much wider distribution of $T_{min}$, but usually required less years of sampling. Differences between these classes were explained by differences in interannual variability in population size (Fig. \ref{fig:class}). We also examined a subset of populations where life-history characteristics were known. None of these explanatory variables were predictive of the minimum time series length required (Fig. \ref{fig:biological_correlates}).

The minimum time series length required was strongly correlated with trend strength, population variance, and autocorrelation (Fig. \ref{fig:correlates}). This is in line based on our simulations and those of others [@Rhodes2011]. Using a generalized linear model, with a Poisson error structure, all three of these explanatory variables were significant and had large effect sizes (see Table A1). Combined, trend strength, population variance, and autocorrelation account for about `r round(100*(poisson_model$null.deviance - poisson_model$deviance)/(poisson_model$null.deviance),1)`% of the explained deviance, which is similar to $R^2$ [@Zuur2009], in minimum time series length required.

Lastly, we tested model sensitivity by using generalized additive models (GAMs) instead of simple linear regression. Again, we examined the minimum time required to estimate long-term population trends (Fig. \ref{fig:gam_example}). We found that although we obtain a similar distribution of minimum times required for GAMs, the minimum time required for GAMs is on average shorter than for linear regression (Fig. \ref{fig:min_time_dist_gam}).

@@

@@

 \setcounter{figure}{0}
 \renewcommand{\thefigure}{A\arabic{figure}}

### 2017-08-17 writing/manuscript_draft.tex
rewrote results section

\usepackage{float}
\usepackage{setspace}\doublespacing \usepackage{lineno}
\usepackage[firstinits=true,style=authoryear-comp,natbib=true,doi=false,isbn=false,url=false,uniquename=false,uniquelist=false,sorting=none]{biblatex}
\linenumbers

@@

Addresses:\emph{$^1$ Center for Population Biology, University of California-Davis, Davis, California 95616 USA}
\vspace{3 mm}

\(^2\)Corresponding author:
\href{mailto:eawhite@ucdavis.edu}{\nolinkurl{eawhite@ucdavis.edu}}
\vspace{3 mm}

Number of words: X,XXX (less than 4,000 words or 20 pages) \vspace{3 mm}

@@

\section{Abstract}\label{abstract}

Long-term census data are necessary to better understand ecological
processes and make management decisions. However, census data are often
expensive, requiring a lot of time and resources. Little work has
addressed the question: when is a time series of census data long enough
to address a question of interest? We determine the minimum time series
length required to estimate significant increases or decreases in
population abundance. Importantly, we examine the ability to detect a
trend with a set level of statistical power, which is often neglected in
ecological time series analyses. Using a simulation approach, we
demonstrate how the minimum time series length required increases with
weaker trends in abundance and with higher population variability. In
addition, we examine 878 populations of vertebrate species to determine
the minimum time required to detect changes in their abundance. We show
that 10-15 years of continuous monitoring are required in order to
achieve a high level of statistical power. Similar to
simulation-approaches, the minimum time required for field census data
strongly depends on trend strength, population variability, and temporal
autocorrelation. These results point to the importance of sampling
populations over long periods of time. Time series less than 10-15 years
are likely under-powered and potentially misleading.

@@

We also explored how the simulation approach can be applied to more
biologically-realistic population models (Fig. \ref{fig:shark_example}).
More specifically, we determine the minimum time required to estimate
long-term population trends using a stochastic, age-structured model of
lemon shark population dynamics in the Bahamas (White, Nagy, and Gruber
2014). We found that over 27 years of continuous monitoring were needed
in this particular scenario (Fig. \ref{fig:shark_example}). Similar to
the simulation approach decribed above, the minimum time required for
the lemon shark population was strongly dependent on model parameters.

@@

We determined the minimum time series length (\(T_{min}\)) required to
address a particular question of interest. More specifically we asked,
what is the minimum time series length required to determine, via linear
regression, the long-term population trend? Here, the minimum time
series length required had high enough statistical power (greater than
0.8) for a set significance level of 0.05. We investigated this question
through two approaches: simulation-based and empirical analyses. We
briefly describe results from the simulation approach and then discuss
our empirical approach.

@@

We constructed a general population model where the trend (i.e.~slope
coefficient) over time could be a model parameter. We chose a simple
model, but any other population model could be used (Fig.
\ref{fig:min_time_dist_log_pop}). Ideally, the specific model choice
should be tailored to the population of interest. We then ran simulated
time series of different lengths. From these simulations we determined
the minimum time series length required to achieve a certain level of
statistical power. We were also able to alter the parameter values
(trend strength and population variability) of the population model to
see how this altered \(T_{min}\) (Fig. \ref{fig:theoretical_approach}).

In line with past work (Gerrodette 1987), we found the \(T_{min}\)
increases (i.e.~more time is required) with decreases in trend strength
and with increases in variability (Fig. \ref{fig:theoretical_approach}).

@@

We examined a database of 878 separate population time series
representing 478 species. This database consists of species with a
variety of life history characteristics. We limited our analyses to
populations with at least 35 years of continuous sampling. We examined
the minimum time required to estimate long-term trends via linear
regression.

Across all the populations we examined, we found an average minimum time
series length required (\(T_{min}\)) of 16.5 (\(\sigma\)=8.4), with a
wide distribution (Fig. \ref{fig:min_time_dist}). In addition, as
expected based on our simulation results and those of others (Rhodes and
Jonzen 2011), the minimum time series length required is strongly
correlated with trend strength, population variance, and autocorrelation
(Fig \ref{fig:correlates}). Using a generalized linear model, with a
Poisson error structure, all three of these explanatory variables were
significant and had large effect sizes (see Table S1). Combined, trend
strength, population variance, and autocorrelation account for about
72.6 of the explained deviance, which is similar to \(R^2\) (Zuur et al.
2009), in minimum time series length required.

We also examined a subset of populations where more explanatory
variables were known (e.g.~body mass, longevity, location). None of
these explanatory variables were predictive of the minimum time series
length required (Fig. \ref{fig:biological_correlates}). Some differences
in \(T_{min}\) did occur between biological class (Fig.
\ref{fig:class}), but this can be attributed to the amount populations
are known to fluctuate (i.e.~the variability in population size).

@@

ERW was partially supported by a National Science Foundation Graduate
Fellowship. We would like to thank members of the Ecological Theory
group at the University of California, Davis for their insight. We would
also like to thank T. Dallas and E. Malcolm-Whitefor their helpful
comments.

>>>>

\usepackage{float} \usepackage{lineno}
\usepackage[firstinits=true,style=authoryear-comp,natbib=true,doi=false,isbn=false,url=false,uniquename=false,uniquelist=false,sorting=none]{biblatex}
\linenumbers

@@

Address:\emph{
    \\$^1$Center for Population Biology \\
    University of California, Davis \\
    2320 Storer Hall \\
        University of California, Davis \\
        One Shields Avenue Davis, CA, USA} \vspace{3 mm}

\(^2\)Corresponding author:
\href{mailto:eawhite@ucdavis.edu}{\nolinkurl{eawhite@ucdavis.edu}}, 1
480 203 7931 \vspace{3 mm}

Number of words (including 300 words for figures): X,XXX Number of
figures: Number of figures in supplementary material: \vspace{3 mm}

@@

\begin{abstract}
Long-term census data are necessary to better understand ecological processes and make management decisions. However, census data are often expensive, requiring a lot of time and resources. Little work has addressed the question: when is a time series of census data long enough to address a question of interest? <!--Here, we explore two approaches to address this question: simulations and an empirical approach.--> We determine the minimum time series length required to estimate significant increases or decreases in population abundance. Importantly, we examine the ability to detect a trend with a set level of statistical power, which is often neglected in ecological time series analyses. Using a simulation approach, we demonstrate how the minimum time series length required increases with weaker trends in abundance and with higher population variability. In addition, we examine 878 populations of vertebrate species to determine the minimum time required to detect changes in their abundance. We show that 10-15 years of continuous monitoring are required in order to achieve a high level of statistical power. Similar to simulation-approaches, the minimum time required for field census data strongly depends on trend strength, population variability, and temporal autocorrelation. <!--Perhaps surprisingly, the minimum time required did not correlate well with biological explanatory variables, like body size or generation length.--> These results point to the importance of sampling populations over long periods of time. <!--We stress the need for verifying a study has enough statistical power to accurately determine long-term population trends.--> Time series less than 10-15 years are likely under-powered and potentially misleading.
\end{abstract}

@@

@@

We determined the minimum time series length (\(T_{min}\)) required to
address a particular question of interest. What is the minimum time
series length required to determine, via linear regression, the
long-term population trend? Here, the minimum time series length
required had high enough statistical power (\(1-\beta\) greater than
0.8) for a set significance level (\(\alpha\)) of 0.05. It is also
possible to alter \(1-\beta\) and \(\alpha\). Predictably, as we
increased our level of power or decreased \(\alpha\), \(T_{min}\)
increased (Fig. \ref{fig:min_time_vs_alpha_beta}). We investigated this
question through two approaches. We briefly describe results from the
simulation approach and then discuss our empirical approach.

@@

We constructed a general population model where the trend strength
(i.e.~slope coefficient) over time could be a model parameter. We then
ran simulated time series of different lengths. From these simulations
we determined the minimum time series length required to achieve a
certain level of statistical power. In line with past work (Gerrodette
1987), we found the \(T_{min}\) increases (i.e.~more time is required)
with decreases in trend strength and with increases in population
variability (Figs. \ref{fig:theoretical_approach}c,d).

We chose a simple model, but any other population model could be used
(see example in Fig. \ref{fig:min_time_dist_log_pop}). Ideally, the
specific model choice should be tailored to the population of interest.
We explored how the simulation approach can be applied to more
biologically-realistic population models (Fig. \ref{fig:shark_example}).
More specifically, we determined the minimum time required to estimate
long-term population trends using a stochastic, age-structured model of
lemon shark population dynamics in the Bahamas (White, Nagy, and Gruber
2014). We found that over 27 years of continuous monitoring were needed
in this particular scenario (Fig. \ref{fig:shark_example}). Similar to
the simulation approach decribed above, the minimum time required for
the lemon shark population was strongly dependent on model parameters.

@@

We examined a database of 878 separate population time series
representing 478 species. This database consists of vertebrate species
with a variety of life history characteristics (Fig.
\ref{fig:biological_correlates}). We limited our analyses to populations
with at least 35 years of continuous sampling. We then examined the
minimum time required to estimate long-term trends via linear
regression.

Across all the populations we examined, we found an average minimum time
series length required (\(T_{min}\)) of 16.5 (\(\sigma\)=8.4), with a
wide distribution (Fig. \ref{fig:min_time_dist}). Estimates of
\(T_{min}\) varied between biological class (Fig.
\ref{fig:min_time_dist}). Ray-finned fish (class Actinopterygii)
typically had estimates of \(T_{min}\) over 20 years. Birds (class Aves)
had a much wider distribution of \(T_{min}\), but usually required less
years of sampling. Differences between these classes were explained by
differences in interannual variability in population size (Fig.
\ref{fig:class}). We also examined a subset of populations where
life-history characteristics were known. None of these explanatory
variables were predictive of the minimum time series length required
(Fig. \ref{fig:biological_correlates}).

The minimum time series length required was strongly correlated with
trend strength, population variance, and autocorrelation (Fig.
\ref{fig:correlates}). This is in line based on our simulations and
those of others (Rhodes and Jonzen 2011). Using a generalized linear
model, with a Poisson error structure, all three of these explanatory
variables were significant and had large effect sizes (see Table A1).
Combined, trend strength, population variance, and autocorrelation
account for about 72.6\% of the explained deviance, which is similar to
\(R^2\) (Zuur et al. 2009), in minimum time series length required.

Lastly, we tested model sensitivity by using generalized additive models
(GAMs) instead of simple linear regression. Again, we examined the
minimum time required to estimate long-term population trends (Fig.
\ref{fig:gam_example}). We found that although we obtain a similar
distribution of minimum times required for GAMs, the minimum time
required for GAMs is on average shorter than for linear regression (Fig.
\ref{fig:min_time_dist_gam}).

@@

ERW was partially supported by a National Science Foundation Graduate
Fellowship. We would like to thank members of the Ecological Theory
group at the University of California, Davis for their insight. We would
also like to thank T. Dallas and E. Malcolm-White for their helpful
comments.

### 2017-08-17 writing/supp_mat_draft.Rmd
small changes in refs of figures
rewrote results section

---
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: true
fontsize: 12pt
geometry: margin=1in
bibliography: White_bib.bib
header-includes: 
    \usepackage{float}
    \renewcommand{\thepage}{S\arabic{page}} 
    \renewcommand{\thesection}{S\arabic{section}}  
    \renewcommand{\thetable}{S\arabic{table}}  
    \renewcommand{\thefigure}{S\arabic{figure}}
    \usepackage[round]{natbib} \bibpunct[; ]{(}{)}{,}{a}{}{;}
---

@@

Code for all the figures and tables can be found at (https://github.com/erwhite1).

@@

In the main text, we explained how the minimum time required strongly correlated with the trend strength, temporal autocorrelation, and variance in population size. Here, we use a generalized linear model framework with a Poisson error structure to determine drivers of the minimum time required. In figure, \ref{fig:poisson_model} we show a set of residual plots for the regression. We then show the coefficient estimates and levels of significance in table \ref{table:model_output}.

>>>>

---
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: true
fontsize: 12pt
geometry: margin=1in
bibliography: White_bib.bib
header-includes: 
    \usepackage{float}
    \renewcommand{\thepage}{S\arabic{page}} 
    \renewcommand{\thesection}{S\arabic{section}}  
    \renewcommand{\thetable}{A\arabic{table}}  
    \renewcommand{\thefigure}{A\arabic{figure}}
    \usepackage[round]{natbib} \bibpunct[; ]{(}{)}{,}{a}{}{;}
---

@@

Data and code for all the figures and tables can be found at (https://github.com/erwhite1).

@@

In the main text, we explained how the minimum time required strongly correlated with the trend strength, temporal autocorrelation, and variance in population size. Here, we use a generalized linear model framework with a Poisson error structure to determine drivers of the minimum time required. In figure \ref{fig:poisson_model}, we show a set of residual plots for the regression. We then show the coefficient estimates and levels of significance in table \ref{table:model_output}.
